A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 6_validation.tex
better width legends
remove gMAT print for now

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Centered}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading schemes.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

@@

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Centered}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The centered scheme shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Centered}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.pdf}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading schemes.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

@@

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Centered}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The centered scheme shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}
